# Conditionals

## if statements

```{r}
# make a modification to this function
k_c <- function(temp_k) {
    if (temp_k < 0) {
        warning('you passed in a negative Kelvin number')
        # stop()
        return(NA)
    }
    temp_c <- temp_k - 273.15
    return(temp_c)
}
```

```{r}
k_c(-9)
```

Our current function does not deal with missing numbers
```{r, eval=FALSE}
k_c(NA)
```

```
Error in if (temp_k < 0) { : missing value where TRUE/FALSE needed
```

```{r}
k_c(0)
```


## If else statements

```{r}

k_c <- function(temp_k) {
    if (temp_k < 0) {
        warning('you passed in a negative Kelvin number')
        # stop()
        return(NA)
    } else {
        temp_c <- temp_k - 273.15
        return(temp_c)
    }
}
```

```{r}
k_c(-9)
```

Our current function does not deal with missing numbers
```{r, eval=FALSE}
k_c(NA)
```

```{r}
k_c(0)
```

## Dealing with NA

Re-write our function to work with missing values.

Note you need to make the `NA` check first.

```{r}
k_c <- function(temp_k) {
    if (is.na(temp_k)) {
        return(NA)
    } else if (temp_k < 0) {
        warning('you passed in a negative Kelvin number')
        # stop()
        return(NA)
    } else {
        temp_c <- temp_k - 273.15
        return(temp_c)
    }
}
```

```{r}
k_c(-9)
```

```{r}
k_c(NA)
```

```{r}
k_c(0)
```

```{r}
if (c(TRUE, FALSE)) {}
```

```{r, error=TRUE}
if (NA) {}
```

use `&&` and `||` to short-circuit the boolean comparisons.
This will also guarantee a value of length `1L`.
`==` is also vectorized, should use `identical()` or `all.equal()`.

`identical` is very strict. Doesn't corece types.

```{r}
identical(0L, 0)
```

`all.equal` has ability to set tolerances.

`all.equal`: compare R objects x and y testing ‘near equality’. If they are different, comparison is still made to some extent, and a report of the differences is returned. Do not use all.equal directly in if expressions—either use isTRUE(all.equal(....)) or identical if appropriate.

```{r}
all.equal(0L, 0)
```

```{r}
if (isTRUE(all.equal(0L, 0))) {print("Hello")}
```

## Fizzbuzz

```{r}
fizzbuzz <- function(x) {
  # these two lines check that x is a valid input
  stopifnot(length(x) == 1)
  stopifnot(is.numeric(x))
  if (!(x %% 3) && !(x %% 5)) {
    "fizzbuzz"
  } else if (!(x %% 3)) {
    "fizz"
  } else if (!(x %% 5)) {
    "buzz"
  } else {
    # ensure that the function returns a character vector
    as.character(x)
  }
}

```


```{r}
fizzbuzz(6)
```

Check modulo 3 only once

```{r}
fizzbuzz2 <- function(x) {
  # these two lines check that x is a valid input
  stopifnot(length(x) == 1)
  stopifnot(is.numeric(x))
  if (!(x %% 3)) {
    if (!(x %% 5)) {
      "fizzbuzz"
    } else {
      "fizz"
    }
  } else if (!(x %% 5)) {
    "buzz"
  } else {
    # ensure that the function returns a character vector
    as.character(x)
  }
}
```

```{r}
fizzbuzz(6)
```

### Vectorized conditionals


```{r}
library(dplyr)

fizzbuzz_vec <- function(x) {
  dplyr::case_when(
    !(x %% 3) & !(x %% 5) ~ "fizzbuzz",
    !(x %% 3) ~ "fizz",
    !(x %% 5) ~ "buzz",
    TRUE ~ as.character(x)
  )
}

```

```{r, error=TRUE}
fizzbuzz(1:10)
```

```{r}
fizzbuzz_vec(1:10)
```


### Multiple conditions

```r
if (this) {
  # do that
} else if (that) {
  # do something else
} else {
  # 
}
```

#### switch

```{r}
calc_op <- function(x, y, op) {
  switch(op,
         plus = x + y,
         minus = x - y,
         times = x * y,
         divide = x / y,
         stop("Unknown op!")
  )
}
```

```{r}
calc_op(10, 20, "times")
```

```{r}
calc_op(10, 20, "divide")
```

#### cut

```{r}
describe_temp <- function(temp) {
  if (temp <= 0) {
    "freezing"
  } else if (temp <= 10) {
    "cold"
  } else if (temp <= 20) {
    "cool"
  } else if (temp <= 30) { 
    "warm"
  } else {
    "hot"
  }
}
```

```{r}
describe_temp(16)
```

Current function can't handle vectors

```{r}
describe_temp(c(16, 61))
```

How cut works:

```{r}
values <- -10:10
values
```

```{r}
cut(values, c(-Inf, -5, -1, 1, 7, Inf))
```

```{r}
cut(values, c(-Inf, -5, -1, 1, 7, Inf), labels = LETTERS[1:5], right = TRUE)
```

```{r}
cut(values, c(-Inf, -5, -1, 1, 7, Inf), labels = LETTERS[1:5], right = FALSE)
```

## Exercise

1. Rewrite the function using `cut`

```{r}
describe_temp <- function(temp) {
  if (temp <= 0) {
    "freezing"
  } else if (temp <= 10) {
    "cold"
  } else if (temp <= 20) {
    "cool"
  } else if (temp <= 30) {
    "warm"
  } else {
    "hot"
  }
}
```

2. How do you indicate `<` and `<=`?
