# Iteration

## Broadcasting

```{r}
f_values <- c(0, 32, 212, -40)
```

```{r}
f_values * 10
```

```{r}
f_values * c(10, 100)
```

## For loops

Temp conversion functions

```{r}
f_k <- function(f_temp) {
    ((f_temp - 32) * (5 / 9)) + 273.15
}


k_c <- function(temp_k) {
    if (is.na(temp_k)) {
        return(NA)
    } else if (temp_k < 0) {
        warning('you passed in a negative Kelvin number')
        # stop()
        return(NA)
    } else {
        temp_c <- temp_k - 273.15
        return(temp_c)
    }
}

f_c <- function(temp_f) {
    temp_k <- f_k(temp_f)
    temp_c <- k_c(temp_k)
    return(temp_c)
}
```



```{r}
for (pizza in f_values) {
    print(pizza)
    converted <- f_c(pizza)
    print(converted)
}
```

```{r}
# 1:length(f_values)
# seq_along(f_values)
for (i in seq_along(f_values)) {
    print(i)
    val <- f_values[i]
    print(val)
    
    converted <- f_c(val)
    print(converted)
}
```

### Pre allocating in a loop

```{r}
# prepopulate an empty vector
converted_values <- vector("double", length(f_values))
for (to_be_converted_position in seq_along(f_values)) {
    converted <- f_c(to_be_converted_position)
    converted_values[to_be_converted_position] <- converted
}
```


```{r}
converted_values
```

## purrr (map)

```{r}
library(purrr)
```

```{r}
map(f_values, f_c)
```

```{r}
map_dbl(f_values, f_c)
```

```{r}
mtcars
```

```{r}
map(mtcars, class)
```

```{r}
map_chr(mtcars, class)
```


```{r}
map_dbl(mtcars, mean)
```

```{r}
map(mtcars, summary)
```


### Exercise

1. Compute the mean of every column in mtcars.
2. Determine the type of each column in nycflights13::flights.
3. Compute the number of unique values in each column of iris.
(Hint: you may want to write a function)
4. Generate 10 random normals from distributions with means of -10, 0, 10, and 100.

#### Solutions

```{r}
# 1. Compute the mean of every column in mtcars
purrr::map_dbl(mtcars, mean)
```

```{r, error=TRUE}
# 2. Determine the type of each column in nycflights13::flights.
purrr::map_chr(nycflights13::flights, class)
```

```{r}
purrr::map(nycflights13::flights, class)
```

```{r}
# Compute the number of unique values in each column of iris.
count_unique <- function(x) {
    return(length(unique(x)))
}

purrr::map_int(iris, count_unique)
```

```{r}
purrr::map_int(iris, function(x) length(unique(x)))
```

```{r}
purrr::map_int(iris, ~ length(unique(.)))
```

```{r}
# Generate 10 random normals from distributions with means of -10, 0, 10, and 100.
purrr::map(c(-10, 0, 10, 100), ~ rnorm(n = 10, mean = .))
```

## Fitting models

```{r}
models <- mtcars %>% 
  split(.$cyl) %>% 
  map(function(df) lm(mpg ~ wt, data = df))
```

```{r}
models %>%
    map(summary) %>%
    map_dbl(~ .$r.squared)
```

```{r}
models %>%
    map_df(broom::tidy)
```

## Apply (in base R)

apply family of functions


### lapply

```{r}
lapply(f_values, f_c)
```

### sapply

```{r}
sapply(f_values, f_c)
```

### vapply

```{r}
vapply(f_values, f_c, numeric(1))
```


### mapply

```{r}
v1 <- c(1, 2, 3, 4)
v2 <- c(100, 200, 300, 400)
```

```{r}
my_mean <- function(x, y){
    return((x + y) / 2)
}
```

```{r}
# sapply(v1, v2, my_mean)
```

```{r}
mapply(my_mean, v1, v2)
# this is the same as purrr::map2
```

### apply (2-dimensions)

```{r}
apply(mtcars, MARGIN = 1, mean)
```

```{r}
apply(mtcars, MARGIN = 2, mean)
```

## Safely dealing with failure

`safely` 
is a function that takes a function, and returns a modified version of that function.
Like how decorators work in Python.

```{r}
safe_log <- safely(log)
```

```{r}
safe_log(10)
```

```{r}
safe_log("a")
```


```{r}
x <- list(1, 10, "a")
y <- x %>% map(safely(log))
```

```{r}
str(y)
```

You can specify the error value

```{r}
safe_log <- safely(log, otherwise = NA)
x <- list(1, 10, "a")
y <- x %>% map(safe_log)
```

Extract values out manually
```{r}
y %>% purrr::map_dbl(magrittr::extract(1))
```

Use the transpose function

```{r}
y <- y %>% purrr::transpose()
str(y)
```

```{r}
y$result %>% purrr::flatten_dbl()
```

## Possibly and quietly succeeds

Possibly always succeeds by giving it a default value.
Safely defaults to `NULL`,
possibly requres the `otherwise` parameter

```{r}
x <- list(1, 10, "a")
x %>% map_dbl(possibly(log, NA_real_))
```

quietly captures output, messages, and warnings, instead of errors

```{r}
x <- list(1, -1)
x %>% map(quietly(log)) %>% str()
```

```{r}
x %>% map(quietly(log)) %>% purrr::transpose() %>% str()
```

## Mapping over different arguments

`map2` and `pmap`

varying just a single value

```{r}
mu <- list(5, 10, -3)
mu %>% 
  map(rnorm, n = 5) %>% 
  str()
```

varying both mu and sigmna

```{r}
sigma <- list(1, 5, 10)

map2(mu, sigma, rnorm, n = 5) %>% str()
```

variying across mu, sigma, and n

```{r}
n <- list(1, 3, 5)

args <- list(mean = mu, sd = sigma, n = n)
```

```{r}
pmap(args, rnorm) %>% str()
```

If your data is all the same length it can be stored in a dataframe.
Or if you have a dataframe of values you are planning to "apply" over.

```{r}
library(tibble)
params <- tribble(
  ~mean, ~sd, ~n,
    5,     1,  1,
   10,     5,  3,
   -3,    10,  5
)
params %>% 
  pmap(rnorm)
```

Having a dataframe and using list columns, you can change
the function an it's arguments with `invoke_map`

```{r}
f <- c("runif", "rnorm", "rpois")
param <- list(
  list(min = -1, max = 1), 
  list(sd = 5), 
  list(lambda = 10)
)
```

```{r}
invoke_map(f, param, n = 5) %>% str()
```

```{r}
library(dplyr)
sim <- tribble(
  ~f,      ~params,
  "runif", list(min = -1, max = 1),
  "rnorm", list(sd = 5),
  "rpois", list(lambda = 10)
)
sim_invoked <- sim %>% 
  mutate(sim = invoke_map(f, params, n = 10))
```

```{r}
sim_invoked
```

```{r}
sim_invoked$sim
```

## Exercise

Write a pipeline that caclculates the mean of each simulation

```{r}
sim_invoked %>%
    mutate(estimate = map_dbl(sim, mean))
```

## Walk

the `map` set of functions return function values,
you use `walk` if you are only interested in the function side effects.
E.g., saving out to a file.


```{r}
x <- list(1, "a", 3)

x %>% 
  walk(print)
```

list of plots with file names, you can use pwalk to save

```{r}
library(ggplot2)
plots <- mtcars %>% 
  split(.$cyl) %>% 
  map(~ggplot(., aes(mpg, wt)) + geom_point())
paths <- stringr::str_c(names(plots), ".pdf")

# pwalk(list(paths, plots), ggsave, path = tempdir())
```

## Other predicates

`keep`, `discard`

only keeps or discards `TRUE` values

```{r}
iris %>% 
  keep(is.factor) %>% 
  str()
```

`some` and `every` work like `any` and `all`

```{r}
x <- list(1:5, letters, list(10))

x %>% 
  some(is_character)
```

`detect` and `detect_index` finds the first element


```{r}
x <- sample(10)
x
```

```{r}
x %>% 
  detect(~ . > 5)
```

`head_while` `tail_while` returns the head or tail while something is true

```{r}
x
```


```{r}
x %>% 
  head_while(~ . > 5)
```

```{r}
x %>% 
  tail_while(~ . > 5)
```

`reduce` applies a function until there is only one left.
Useful for repeadily joinging dataframes together

```{r}
dfs <- list(
  age = tibble(name = "John", age = 30),
  sex = tibble(name = c("John", "Mary"), sex = c("M", "F")),
  trt = tibble(name = "Mary", treatment = "A")
)

dfs
```

```{r}
dfs %>% reduce(full_join)
```

