# Linear Models

## Fit a linear model

### Base R
```{r}
library(AmesHousing)
```

```{r}
ames <- AmesHousing::make_ames()
```


```{r}
# Gr Liv Area = Above grade (ground) living area square feet
lm_ames <- lm(Sale_Price ~ Gr_Liv_Area, data = ames)
```

```{r}
lm_ames
```

```{r}
broom::tidy(lm_ames)
```

### Tidymodels

Steps in a parsnip model:

1. Pick a model
2. Set the engine (what library is running the model)
3. Set the mode (if needed, e.g., regression or classification)

List of models: https://tidymodels.github.io/parsnip/articles/articles/Models.html

Allows you to quickly swap out and try different models

```{r}
library(parsnip)
```

```{r}
lm_spec <- parsnip::linear_reg() %>%
  parsnip::set_engine(engine = "lm")
```

Train/fit the model:

```{r}
lm_fit <- parsnip::fit(lm_spec, Sale_Price ~ Gr_Liv_Area, data = ames)
lm_fit
```

```{r}
broom::tidy(lm_fit)
```

## Predict

```{r}
price_pred <- stats::predict(lm_fit, new_data = ames)
price_pred
```

```{r}
price_pred <- price_pred %>%
  dplyr::mutate(truth = ames$Sale_Price)
```

```{r}
price_pred
```

## Error metrics

$$
\begin{aligned}
\text{MAE}  &= \dfrac{1}{n}\sum_{i=1}^{n} \left| \hat{y}_i - y_i \right|\\
\text{RMSE} &= \sqrt{\dfrac{1}{n}\sum_{i=1}^{n} \left( \hat{y}_i - y_i \right)^2}
\end{aligned}
$$

Regression Metrics Guide: https://www.h2o.ai/blog/regression-metrics-guide/

```{r}
library(yardstick)

yardstick::rmse(price_pred, truth = truth, estimate = .pred)
```

## Train Test Split

- best way to measure model performance is to see how it performs to *new data*

http://www.feat.engineering/

train-test-split

```{r}
ames_split <- rsample::initial_split(ames, prop = 0.75)
ames_split
```

```{r}
dim(ames)
```

```{r}
class(ames_split)
```
 
```{r}
ames_train <- rsample::training(ames_split)
```

```{r}
ames_test <- rsample::testing(ames_split)
```

## Exercise


1. Split the `ames` dataset into training and testing sets
2. Fit a linear model
3. Measure how the model is performing

- Hint: set a seed (e.g., 42)
- Hint: `library(tidyverse)`, `library(tidymodels)`

### Solution

```{r}
library(tidyverse)
library(tidymodels)
set.seed(42)

ames_split <- rsample::initial_split(ames)
```

```{r}
ames_train <- rsample::training(ames_split)
ames_test <- rsample::testing(ames_split)
```

```{r}
lm_fit <- parsnip::linear_reg() %>%
  parsnip::set_engine(engine = "lm") %>%
  parsnip::fit(Sale_Price ~ Gr_Liv_Area, data = ames_train)
```

```{r}
price_pred <- lm_fit %>%
  stats::predict(new_data = ames_test) %>%
  dplyr::mutate(price_truth = ames_test$Sale_Price)
```

```{r}
yardstick::rmse(price_pred, truth = price_truth, estimate = .pred)
```
