# Workflows

1. Transform data: center/scale `Sale_price`
2. Split data
3. Train on the training set
4. Evaluate/predict on the test set

Data Leakage: When information from the test set "leaks" into the training data

1. Split data
2. Transform training set
3. Train on training set
4. Transformation + Evaluate/predict on test set

```{r}
library(AmesHousing)
library(tidymodels)
```

```{r}
lm_spec <- parsnip::linear_reg() %>%
  parsnip::set_engine("lm")
```

```{r}
ames_split <- rsample::initial_split(AmesHousing::make_ames(), prop = 0.75)
```

```{r}
bb_wf <- workflows::workflow() %>%
  workflows::add_formula(Sale_Price ~ Bedroom_AbvGr + Full_Bath + Half_Bath) %>%
  workflows::add_model(lm_spec)
```

```{r}
bb_wf
```

```{r}
# fit the final best model to the training set and evaluate the test set
fit_split <- tune::last_fit(bb_wf, ames_split)
fit_split
```

```{r}
fit_split %>% tune::collect_metrics()
```

## Update formula

```{r}
all_wf <- bb_wf %>%
  workflows::update_formula(Sale_Price ~ .)

all_wf %>%
  tune::last_fit(ames_split) %>%
  tune::collect_metrics()
```

## Update Model

Update to fit a regression decision tree

```{r}
rt_spec <- 
  parsnip::decision_tree() %>%
  parsnip::set_engine(engine = "rpart") %>% 
  parsnip::set_mode("regression")
```

```{r}
rt_wf <- 
  all_wf %>% 
  workflows::update_model(rt_spec)
```

```{r}
all_fitwf <- rt_wf %>%
  tune::last_fit(ames_split)

all_fitwf %>%
  tune::collect_metrics()
```

```{r}
all_fitwf %>% tune::collect_predictions()
```

## Get workflow components

```{r}
all_fitwf %>%
  purrr::pluck(".workflow", 1) %>%
  workflows::pull_workflow_fit() # return parsnip model fit
```

```{r}
all_fitwf %>%
  purrr::pluck(".workflow", 1) %>%
  workflows::pull_workflow_spec()
```
