# Purrr + tidymodel objects

```{r}
library(tidyverse)
library(tidymodels)
library(AmesHousing)
```


## Exercise: Train on split data

```{r}
ames <- AmesHousing::make_ames()
```

```{r}
ames_split <- rsample::initial_split(ames,
                                    strata = Sale_Price,
                                    breaks = 4)
```

```{r}
ames_train  <- training(ames_split)
ames_test   <- testing(ames_split)
```

```{r}
lm_spec <- parsnip::linear_reg() %>%
  parsnip::set_engine("lm")

lm_fit <- workflows::workflow() %>%
  workflows::add_formula(Sale_Price ~ Gr_Liv_Area) %>%
  workflows::add_model(lm_spec) %>%
  parsnip::fit(data = ames_train)
```

```{r}
price_pred <- lm_fit %>%
  stats::predict(new_data = ames_test) %>%
  dplyr::mutate(price_truth = ames_test$Sale_Price)
```

```{r}
yardstick::rmse(price_pred, truth = price_truth, estimate = .pred)
```
## Pass the split object

```{r}
lm_split <- workflows::workflow() %>%
  workflows::add_formula(Sale_Price ~ Gr_Liv_Area) %>%
  workflows::add_model(lm_spec) %>%
  tune::last_fit(ames_split)
  
```

```{r}
lm_split
```

## Question

1. What does the `splits` column contain

```{r}
simple_split <- lm_split %>%
  dplyr::select(splits, id)
```

```{r}
simple_split
```

## Exercise

1. How can you just return the contents of the first cell in splits?

```{r}
simple_split[["splits"]][[1]]
simple_split[[1, 1]]
simple_split %>% magrittr::extract2("splits") %>% 
  magrittr::extract2(1)
simple_split %>% purrr::pluck("splits", 1)

```

2. What's the difference between the output of these 2 results?

```{r}
simple_split %>%
  pluck("splits")
```

```{r}
simple_split %>%
  pluck("splits", 1)
```

## `map` functions

```{r}
simple_split %>%
  pluck("splits") %>%
  map(rsample::testing)
```

## Exercise

Create a column in `simple_split` that contains
the training set data frame. Name the column `train_set`.

```{r}
simple_split %>%
  dplyr::mutate(train_set = purrr::map(splits, training))
```

## `unnest`

Expanding a list column

```{r}
simple_split %>%
  dplyr::mutate(train_set = purrr::map(splits, training)) %>%
  tidyr::unnest(train_set)
```

```{r}
lm_split
```

```{r}
lm_split %>%
  tidyr::unnest(.metrics)
```

`collect_metrics` is a shortcut.

```{r}
lm_split %>% tune::collect_metrics()
```
