# Recipes

The pre-processing step

https://tidymodels.github.io/recipes/reference/index.html

```{r}
library(tidymodels)
library(AmesHousing)
```

```{r}
ames <- AmesHousing::make_ames()
```

```{r}
rec <- recipes::recipe(Sale_Price ~ ., data = ames)
```

```{r}
rec %>% 
  step_novel(all_nominal()) %>%
  step_zv(all_predictors())
```

## PCA

```{r}
rec <- recipes::recipe(Sale_Price ~ .,
                       data = ames) %>%
  recipes::step_center(all_numeric()) %>% 
  recipes::step_scale(all_numeric())
```

### Prep/bake

- `prep`: trains a dataset
- `bake`: apply a trained model to new data

However, you do not need to do this since the `fit` functions do this for you too

```{r}
rec %>%
  recipes::prep(training = ames) %>%
  recipes::bake(new_data = ames)
```

### Dummy variables

- aka one-hot encoding
- You don't need this for decision trees or ensembles of trees

```{r}
rec %>%
  recipes::step_dummy(all_nominal())
```

### Step novel

- A catch all for new categories that the model may not have trained on
- Do this before dummy encoding

```{r}
rec %>%
  recipes::step_novel(all_nominal()) %>%
  recipes::step_dummy(all_nominal())
```

### remove 0 variance

- Remove columns where there is only 1 value in it

```{r}
rec %>%
  recipes::step_novel(all_nominal()) %>%
  recipes::step_dummy(all_nominal()) %>%
  recipes::step_zv(all_predictors())
```

### PCA

```{r}
rec %>%
  recipes::step_novel(all_nominal()) %>%
  recipes::step_dummy(all_nominal()) %>%
  recipes::step_zv(all_predictors()) %>%
  recipes::step_pca(all_numeric(), num_comp = 5)
```

## Exercise

Write a recipe for the `Sale_Price ~ .` variables that:

1. Adds a novel level to all factors
2. Converts all factors to dummy variables
3. Catches any zero variance variables
4. Centers all of the predictors
5. Scales all of the predictors
6. Computes the first 5 principal components

Save the result as `pca_rec`

### Solution

```{r}
pca_rec <-
  recipe(Sale_Price ~ ., data = ames) %>%
  step_novel(all_nominal()) %>%
  step_dummy(all_nominal()) %>%
  step_zv(all_predictors()) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_pca(all_predictors(), num_comp = 5)
```

## Put it all together

1. Split the ames data (rsample)
2. Create a `lm_spec` (parsnip)
3. Create a `pca_rec` recipe (recipe)
4. Create a workflow (workflows)
5. Fit model (tune)

### Solution

```{r}
ames_split <- rsample::initial_split(ames)
ames_train <- rsample::training(ames_split)
ames_test <- rsample::testing(ames_split)
```


```{r}
lm_spec <- parsnip::linear_reg() %>%
  parsnip::set_engine("lm")
```

```{r}
pca_rec <-
  recipe(Sale_Price ~ ., data = ames_train) %>%
  step_novel(all_nominal()) %>%
  step_dummy(all_nominal()) %>%
  step_zv(all_predictors()) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_pca(all_predictors(), num_comp = 5)
```

```{r}
pca_wf <- workflows::workflow() %>%
  workflows::add_recipe(pca_rec) %>%
  workflows::add_model(lm_spec)
pca_wf
```
```{r}
pca_wf %>%
  tune::last_fit(ames_split) %>%
  tune::collect_metrics()
```
