# Bookdown

https://bookdown.org/yihui/bookdown/

```{r, eval=FALSE}
install.packages("bookdown")
```


Minimal bookdown example:

- Code: https://github.com/rstudio/bookdown-demo
- Site: https://bookdown.org/yihui/bookdown-demo/


## Components of a book

### Section titles:

```
# Preface {-}
```

```
# Part 1: The beginning {-}
```

```
# Chapter 1: Introduction

## Example One

## Example Two
```

## Rendering M-K vs K-M

- M-K: merge all documents first, then knit
- K-M: Knit each document separately, then merge together

- Default is M-K, but you can change this option in `_bookdown.yml`, `new_session: yes` vs `new_session: no`

## Looking at the book while you work

- Preview book add-on
  - Will recompile the book on each save
- 

## Figures

```{r}
library(ggplot2)
```

```{r}
ggplot(diamonds, aes(x = carat, y = price)) +
  geom_point()
```

```{r diamond-colored, fig.cap = 'A figure caption.'}
ggplot(diamonds, aes(x = carat, y = price, color = color)) +
  geom_point()
```

````markdown
` ``{r diamond-colored, fig.cap = 'A figure caption.'}
ggplot(diamonds, aes(x = carat, y = price, color = color)) +
  geom_point()
` ``
````
You can reference Figure \@ref(fig:diamond-colored) by the chunk name with `\@ref(fig:diamond-colored)`

## Tables

```{r, mtcars-head-table}
knitr::kable(
  head(mtcars[, 1:8], 10), booktabs = TRUE,
  caption = 'A table of the first 10 rows of the mtcars data.'
)
```

````markdown
` ``{r, mtcars-head-table}
knitr::kable(
  head(mtcars[, 1:8], 10), booktabs = TRUE,
  caption = 'A table of the first 10 rows of the mtcars data.'
)
` ``
````

Table \@ref(tab:mtcars-head-table) can be referenced with `\@ref(tab:mtcars-head-table)`

## Cross refrence chapters {#cross-ref}

Cross references to other chapters can be done with `\@ref(label)`.
Reference labels are auto created for you,
but it's better to create your own labels with `{#id}`.
E.g., this chapter, Section \@ref(cross-ref), was done by placing `## Cross refrence chapters {#cross-ref}`
as the header.
