---
title: "One R Markdown Document, Fourteen Demos"
author: "Yihui Xie"
date: "2020-01-30 @ rstudio::conf"
bibliography: R-packages.bib
link-citations: true
---

# Introduction

- This is an **R Markdown** document [@R-rmarkdown].
- Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents, etc.
- For more details on using R Markdown, see <https://rmarkdown.rstudio.com>.

# R Markdown

## Embed R code

### Data

You can embed an R code chunk like this:

```{r}
dat <- iris[, 1:2]
names(dat) <- c('x', 'y')
str(dat)
```

## Draw plots

### Starry night

```{r star, fig.width=6, fig.height=3.9}
par(mar = c(4, 4, .1, .2))
smoothScatter(dat)
sunflowerplot(dat, pch = 20, col = 7, seg.col = 7, size = .1, add = TRUE)
```

## Create tables

### A simple table

```{r}
fit <- lm(y ~ x, data = dat)
tab <- coef(summary(fit))  # regression coefficients
knitr::kable(tab, caption = 'A simple table.')
```

## Inline code

### The model

The fitted model is: $$Y = `r tab[1, 1]` + `r tab[2, 1]`X$$ 

# Other features

## Figure caption

You can also add captions and numbers to figures. See Figure \@ref(fig:pie) for example.

```{r pie, fig.cap='My favorite pie chart.', tidy=FALSE, exercise=TRUE}
par(mar = c(0, 1, 0, 1))
pie(
  c(280, 60, 20),
  c('Sky', 'Sunny side of pyramid', 'Shady side of pyramid'),
  col = c('#0292D8', '#F7EA39', '#C4B632'),
  init.angle = -50, border = NA
)
```

## Dynamic content

### Animation

```{r, pacman, animation.hook='gifski', eval=!(knitr:::pandoc_to() %in% 'beamer'), cache=TRUE}
par(mar = c(0, 1, 0, 1))
a = sample(0:359, 1)
for (i in 1:2) {
  pie(c(i %% 2, 6), col = c('red', 'yellow'), labels = NA,
      init.angle = a)
}
```


### Leaflet maps

```{r, map, cache=TRUE, out.width='100%'}
library(leaflet)
leaflet() %>% addTiles() %>% setView(-122.410951, 37.7858188, zoom = 19)
```

### DataTables

```{r, dt, cache=TRUE}
DT::datatable(iris)
```

```{r, include=FALSE}
knitr::write_bib(loadedNamespaces(), file = 'R-packages.bib')
```
